---
title: "exp3BanditDizzys"
author: "TRAN THI CAM GIANG"
date: "September 29, 2015"
output: pdf_document
---

BANDIT EXP3 : 
Exp3 bandit stands for Exponential-weight algorithm for Exploration and Exploitation. It works by maintaining a list of weights for each of the actions, using these weights to decide randomly which action to take next, and increasing (decreasing) the relevant weights when a payoff is good (bad). We further introduce an egalitarianism factor \gamma \in [0,1] which tunes the desire to pick an action uniformly at random. That is, if \gamma = 1, the weights have no effect on the choices at any step.
#Ref: http://jeremykun.com/2013/11/08/adversarial-bandits-and-the-exp3-algorithm/

The structure of the programme :
1. call the package "dizzysNEWYANN" that includes the function simulating stochastically SEIR model according tho the formula \beta of YANN.
2. call the function "getExtRateMETAPOP" in the file "extRateMETAPOP.r". This function simulates the SEIR model of a metapopulation of n subpopulations. After that, this function calculates the survival time of each subpopulation until the end of simulation. We have a censored data. based on the simulation time, we extract the uncensored data and estimate the extinction rate of the metapopulation.
3. call the functions in the file "exp3Bandit.r", it is the main file in this work :
  J' ai écrit les codes de Bandit partielle Exp3
  J'ai modélisé l'algorithme Bandit Exp3 pour notre modèle :
  a. Nombre de tour : basé sur le budget de CPU, ici le temps maximum de simualtion (e.x 100ans)
  b. K bras : K est le nombre de villes dans une métapopulation. Ici, on a K différente métapopulations qui ont le nombre de villes de 1 à K.
  c. Résultat obtenu : c'est une list qui contient deux événement :
	  *) les poinds de chaque métapopulation à chaque tour
	  *). les récompense obtenues de chaque métapopulation à chaque tour.
  d. Fonctionner le programme


```{r}
source(exp3Bandit.r)
ls()
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
